Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
use a unified notation for the two verification engines in sec 3 and 4

@@

For the majority of our benchmarks, the conjecture explained in
section~\ref{synthesis-elements} holds and the inductive back-end is able to
find a stable solution in less than one minute.  This is possible if the
inductive solutions need to be refined with few counterexamples and
fixed-point precision increases.  However, $2$ benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$
in Table~\ref{tab:results}).  In these cases, the interval arithmetic
back-end is able to complement the inductive approach and synthesise a
solution instead, albeit with significantly larger runtimes.  This
performance difference is due to the fact that the interval back-end does
not take advantage of the inductive conjecture inherent to CEGIS, but
instead fully explores the counterexample space.  The result is a
performance difference of at least two orders of magnitude in our
experiments, leading to the interval back-end timing out on the majority of
our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
back-ends for each benchmark, which in $12$ out of $15$ benchmarks is the
inductive back-end.

@@

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the inductive back-end is able to synthesise stable
controllers in the $12$ out of $15$ benchmarks, and can be complemented
using the interval arithmetic back-end for $2$ additional benchmarks, where
the inductive conjectures fail.  Both back-ends together enabled controller
synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark
our approach failed to synthesise a stable controller in the requested time
limits.  This can be addressed by either increasing the fixed point word
widths considered or using floating point arithmetic instead.  A link to the
full experimental environment, including scripts to reproduce the
experiment, all benchmarks and the CEGIS tool is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}

>>>>

In the rest of the paper, we will refer to the two approaches 
for the {\sc verify} phase as one-stage and two-stage, respectively.

@@

For the majority of our benchmarks, the conjecture explained in
Section~\ref{synthesis-elements} holds and the two-stage verification 
engine %inductive back-end 
is able to find a stable solution in less than one minute.  This is possible if the
inductive solutions need to be refined with few counterexamples and
fixed-point precision increases.  However, $2$ benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$
in Table~\ref{tab:results}).  In these cases, the one-stage engine 
%interval arithmetic back-end 
is able to complement the two-stage approach and synthesise a
solution instead, albeit with significantly larger runtimes.  This
performance difference is due to the fact that the one-stage verification engine does
not take advantage of the inductive conjecture inherent to CEGIS, but
instead fully explores the counterexample space.  The result is a
performance difference of at least two orders of magnitude in our
experiments, leading to the one-stage engine timing out on the majority of
our benchmarks.  Table~\ref{tab:results} only lists the faster of the two
verification engines for each benchmark, which in $12$ out of $15$ benchmarks is the
two-stage one.

@@

The median runtime for our benchmark set is $197$\,s, implying that half of
the controllers can be synthesised in less than $5$ minutes using our
present approach.  Overall the average synthesis time amounts to
approximately $30$ minutes.  With respect to RQ2 we consider these times
short enough to be of practical use to control engineers.  Regarding RQ1 we
further conclude that the two-stage verification engine is able to synthesise stable
controllers in the $12$ out of $15$ benchmarks, and can be complemented
using the one-stage engine for $2$ additional benchmarks, where
the inductive conjectures fail.  Both verification engines together enabled controller
synthesis for $14$ out of $15$ benchmarks.  For the $1$ remaining benchmark
our approach failed to synthesise a stable controller in the requested time
limits.  This can be addressed by either increasing the fixed point word
widths considered or using floating point arithmetic instead.  A link to the
full experimental environment, including scripts to reproduce the
experiment, all benchmarks and the CEGIS tool is provided in the
footnote.\footnote{\url{https://drive.google.com/file/d/0ByIexo3Z5N91QkhrMi1rdkZFTWc/view}}
